Using traffic analysis to identify The Second Generation Onion Router

### 2011-02-26 thesis/experiment.tex
Lots more rewriting of methods

  VirtualBox software allows multiple guest operating systems to run in an
  isolated virtual environment on a host operating system \parencite{:fk}.
  It is free software and supports both snapshots and a remote control facility
  which make it useful for running a controlled experiment \parencite{:uq}.

@@

@@

@@

Table \ref{table:hosts} shows the role of each system in the experiment as well
as the edition of operating system in use and the IP address they were
configured with on the network.

\begin{tabular}{lrr}
  \toprule
  Role & Operating System Version & IP Address\\
  \midrule
  Client Host & Desktop & 192.168.0.100\\
  Server Host & Desktop & 192.168.0.001\\
  Tor Host & Desktop & 192.168.0.102\\
  \midrule
  Sniffing System & Server & 192.168.0.200\\
  \midrule
  Client Guest & Desktop & 192.168.0.16\\
  Server Guest & Server & 192.168.0.17\\
  Tor Network Guest & Server & 192.168.0.18\\
  \bottomrule
  \label{table:hosts}
\end{tabular}

Figure \ref{network-diagram} shows the placement of applications and relevant
data flows.

\begin{figure}[H]
  \centering\includegraphics[width=\linewidth]{network-diagram}
  \caption{Network Diagram}
  \label{network-diagram}
\end{figure}

@@

Substituting \verb+eth0+ with the physical network interface identifier as
appropriate, and the address \verb+192.168.0.16+ with the desired value.

@@

The host systems all run an identically configured Ubuntu 10.04 desktop
operating system, except for the IP address which is configured as detailed in
\ref{table:hosts}. To support the guest operating systems, VirtualBox is
required. The procedure for installing VirtualBox is detailed below:

@@

The guest operating system images can then be created or imported from an
external disk.

\subsubsection{Server Host}

One of the host systems is set aside as a management system, which is
responsible for ensuring the experiment runs and restarts it if there are any
problems. On this machine a private SSH key is created, and copied to the
authorized keys file on all other hosts. This allows the management system to
connect to all the other systems and issue commands without user interaction.

The management script runs on the management system to watch the experiment's
progress. This is a simple Ruby script which uses SSH to control the other Host
systems and opens a socket which waits for a connection that indicates that the
experiment has finished. Every time it starts the experiment, it rolls back
each virtual machine to a preconfigured snapshot. If the experiment takes too
long, say because a virtual machine hangs or something is wrong, it will be
started without waiting for the finish condition. Figure
\ref{manager-flow-diagram} contains a diagram which outlines the basic flow of
the manager script.

@@

\subsubsection{Client System}

The client system runs Ubuntu 10.04 Desktop Operating System as well as a
number of applications that allow it to perform automated web browsing. Tor is
configured on this system as well for the Tor part of the experiment but is
initially disabled.

@@

The client operation is controlled by a Ruby script which ensures that the
Selenium-RC server is running, executes a number of Selenium browser
simulations using RSpec and reports it's success by connecting to an open
socket on the management system.

There are 170 simulations which emulate simple website interactions which have
different traffic profiles against 30 different websites on the Server system.

For the non-SSL portion of the experiment, Selenium is configured to use a
special proxy which automatically accepts self signed certificates. Typical
interactions with SSL encrypted websites are signed by a certificate authority,
so no user interaction is required to begin browsing.

@@

SSL + Tor over selenium.

Generate a selenium firefox profile. First launch selenium in interactive mode
specifying a proxy:

\begin{lstlisting}[language=sh]
java -jar $selenium.jar -interactive
\end{lstlisting}

This will start a prompt to which you can edit commands, you must launch a
browser to get selenium to create a firefox profile directory.

\begin{lstlisting}[language=sh]
cmd=getNewBrowserSession&1=*firefoxproxy&2=http://www.google.com
\end{lstlisting}

Generate a firefox profile, then edit the proxy.pac file to

\begin{lstlisting}[language=sh]
function FindProxyForURL(url, host) {
   if(shExpMatch(url, '*/selenium-server/*')) {
       return 'PROXY localhost:4444; PROXY proxy.ourdomain.dom:8080';
   } else if (shExpMatch(host, '*dev.ourdomain.dom*')) {
       return 'DIRECT';
   } else if (shExpMatch(host, '*qa.ourdomain.dom*')) {
       return 'DIRECT';
   } else if (shExpMatch(host, '*staging.ourdomain.dom*')) {
       return 'DIRECT';
   } else {
       return 'PROXY proxy.ourdomain.dom:8080';
   }
}
\end{lstlisting}

or

\begin{lstlisting}[language=sh]
function FindProxyForURL(url, host) {
   if(shExpMatch(host, '*torsim')) {
       return 'PROXY localhost:8118';
   }
   return 'PROXY localhost:4444; DIRECT';
}
\end{lstlisting}

This makes sure that your proxy (Tor) gets used for outgoing connections, and
the selenium proxy is used for running tests.

To get SSL certificates accepted, you must manually accept them permanently for
each host. This will update the \verb+cert_override.txt+ and \verb+cert8.db+
files.

Tor must have the following setting supplied:

\begin{lstlisting}[language=sh]
ExitPolicyRejectPrivate 0
\end{lstlisting}

Since we are using a 192.* network. - Not true, testing mode flag sets this.

@@

\subsubsection{Server System}

The host system runs an apache web server which serves two sets of sample
websites, static and dynamic. The static websites are served each from a
different numbered directory and accessible over a different virtual host. This
means that when a web browser is pointed at the directory
\verb+site1.static.torsim+ the files in
\verb+/var/www/thesis/experiment/simulation/static/site1+ are served to the
browser.

For the SSL part of the experiment, only the HTTPS port 443 is accessed and all
information is sent to the browser using encryption.

The dynamic sample websites change subtly with each attempted access. There are
10 sample websites each a slightly different Ruby Sinatra application.

\subsubsection{Tor Simulation}

The Tor Simulation Guest is responsible for emulating a Tor network. It runs
three Tor directory authorities as well as fifteen relays.

Each Tor instance on the Tor Simulation system is given it's own separate
directory for configuration, logging and temporary files.

Deploy the experiment files.

Install Tor:

\subsubsection{Client System}

Install Ubuntu 10.04 Desktop as in the Host system directions, leaving out the
Virtual Box installation.

\begin{enumerate*}
  \item Deploy the experiment files onto the client system.
  \item Install Ruby
  \item Install the bundler ruby gem with the command:
    \begin{lstlisting}[language=sh]
gem install bundler
    \end{lstlisting}
  \item Install the required client ruby gems by executing the bundler from the client directory in the deployed experiment files.
    \begin{lstlisting}[language=sh]
bundle install
    \end{lstlisting}
  \item Ensure that the client script is executed at system startup.
\end{enumerate*}

\subsubsection{Configuring the Management Script}

Once all systems are deployed, the management script needs to be altered to

@@

Running the experiment is a matter of ensuring all Host systems are powered on,
if everything is configured correctly the experiment will continue to run until
stopped manually.

>>>>

  VirtualBox software allows multiple guest operating systems to run in an
  isolated virtual environment on a host operating system \parencite{:fk}.
  It is free software and supports both snapshots and a remote control facility
  which make it useful for running a controlled experiment \parencite{Oracle:2011kx}.

@@

  \item RSpec

  RSpec is a testing framework for Ruby which allows the creation of examples in
  an easy to read Domain Specific Language (DSL). It is well integrated with
  Selenium which makes it ideal for running large suites of Selenium tests.

@@

The final stage simulation will be run in three phases:

\begin{enumerate*}
  \item Web requests over HTTPS
  \item Web requests over HTTP proxied by Tor
  \item Web requests over HTTPS proxied by Tor
\end{enumerate*}

@@

Table \ref{table:hosts} shows the role, edition of the Ubuntu operating system
installed and the IP address assigned to each host in the experiment network.

\begin{tabular}{lrr}
  \toprule
  Role & Operating System Version & IP Address\\
  \midrule
  Client Host & Desktop & 192.168.0.100\\
  Server Host & Desktop & 192.168.0.101\\
  Tor Host & Desktop & 192.168.0.102\\
  \midrule
  Sniffing System & Server & 192.168.0.200\\
  \midrule
  Client Guest & Desktop & 192.168.0.16\\
  Server Guest & Server & 192.168.0.17\\
  Tor Network Guest & Server & 192.168.0.18\\
  \bottomrule
  \label{table:hosts}
\end{tabular}

Figure \ref{network-diagram} shows the placement of applications and relevant
data flows when running the simulation in HTTPS mode.

\begin{figure}[H]
  \centering\includegraphics[width=\linewidth]{network-diagram}
  \caption{Network Diagram: Phase 1}
  \label{network-diagram}
\end{figure}

Figure \ref{network-diagram-with-tor} shows the network configuration when
running the experiment in HTTP over Tor mode.

\begin{figure}[H]
  \centering\includegraphics[width=\linewidth]{network-diagram-with-tor}
  \caption{Network Diagram: Phase 2}
  \label{network-diagram-with-tor}
\end{figure}

Figure \ref{network-diagram-with-tor-encrypted} shows the network configuration when
running the experiment in HTTPS over Tor mode.

\begin{figure}[H]
  \centering\includegraphics[width=\linewidth]{network-diagram-with-tor-encrypted}
  \caption{Network Diagram: Phase 3}
  \label{network-diagram-with-tor-encrypted}
\end{figure}

@@

Substituting \verb+eth0+ with the physical network interface identifier as
appropriate, and the address \verb+192.168.0.16+ with the desired value. All
systems were assigned IP Addresses as listed in \ref{table:hosts}.

@@

The host systems all run an identically configured Ubuntu 10.04 desktop
operating system, except for the IP address which is configured as described in
\ref{table:hosts}. To support the guest operating systems, VirtualBox is
required. The procedure used to install VirtualBox is described below:

@@

The guest operating systems were copied across using a USB thumb drive and
installed using the VirtualBox import feature.

\subsubsection{Client Host}

One of the host systems was set aside as a management system, which is
responsible for ensuring the experiment runs and restarts it if there are any
problems.

For delivering remote commands from the management system to other hosts without
interactive prompts, SSH is used with automatic private key authentication. To
enable automatic private key authentication, first a private key was generated
by executing the following commands in a terminal prompt:

\begin{enumerate*}
  \item \verb+ssh-keygen+
  \item Press enter to use default keyfile (\verb+/Users/john/.ssh/id_rsa+)
  \item Press enter twice to supply a blank passphrase
\end{enumerate*}

The public key is then copied to the other hosts using secure copy (SCP), for example:
\begin{lstlisting}[language=sh]
  scp ~/.ssh/id_rsa.pub john@192.168.0.101:
\end{lstlisting}

This file was then appended to the authorized hosts file on each system, by
executing the following command from each host system:
\begin{lstlisting}[language=sh]
  cat id_rsa.pub >> ~/.ssh/authorized_keys
\end{lstlisting}

The management script runs on the management system to monitor experiment
progress. This simple script manages the VirtualBox instances on the other hosts
by remotely executing VirtualBox control commands using SSH. It ensures that
each time the experiment is finished, the VirtualBox instances are rolled back
and restarted. If the experiment takes too long, it is manually restarted. The
script listens on a port for a connection from the experiment client which
indicates the experiment has finished. Figure \ref{manager-flow-diagram}
contains a diagram which outlines the basic flow of the manager script.

@@

\subsubsection{Client Guest}

The client system runs Ubuntu 10.04 Desktop Operating System as well as a
number of applications that allow it to perform automated web browsing. Tor is
configured on this system but disabled for the first phase of the simulation.

@@

The client operation is controlled by a Ruby script which ensures that the
Selenium-RC server is running, executes a number of Selenium browser simulations
using RSpec and reports completion by connecting to an open socket on the
management system. This script is configured to run at boot time so that as soon
as the system is powered on the simulation commences. The complete client script
is included in the Appendix, section \ref{client-script}.

The simulation component consists of 170 different RSpec examples which emulate
various profiles of website traffic against 30 different example websites
provided by the Server system.

\paragraph{Tor}
\label{install-tor}

Tor is installed on the client guest using the following procedure:

\paragraph{RSpec}

Each RSpec example specifies the site to test and the directions to send to the
Firefox browser, the first RSpec example is listed below and shows a simple test
which accesses \verb+https://site1.static.torsim/+ and opens the root web page.

\begin{lstlisting}[language=ruby]
require "rubygems"
gem "rspec"
gem "selenium-client"
require "selenium/client"
require "selenium/rspec/spec_helper"

describe "site1.static.torsim.1" do
  attr_reader :selenium_driver
  alias :page :selenium_driver

  before(:all) do
    @verification_errors = []
    @selenium_driver = Selenium::Client::Driver.new \
      :host => "localhost",
      :port => 4444,
      :browser => "*firefoxproxy",
      :url => "https://site1.static.torsim/",
      :timeout_in_second => 60
  end

  before(:each) do
    @selenium_driver.start_new_browser_session
  end

  append_after(:each) do
    @selenium_driver.close_current_browser_session
    @verification_errors.should == []
  end

  it "test_site1.static.torsim.1" do
    page.open "/"
  end
end
\end{lstlisting}

@@

There are a number of concerns with using Selenium and HTTPS as well as self
signed certificates.

Typical websites that provide HTTPS on the world wide web have a server
certificate signed by a trusted authority, so the user is not required to agree
to communicating with a possibly forged website. For the experiment a self
signed certificate was used, which triggers a number of security warnings when
accessed through most modern browsers. To automate acceptance of this security
risk Selenium was configured with a special proxy which implicitly accepts any
self signed certificates. The following steps were used to configure this proxy:

\begin{enumerate*}
  \item A Firefox custom profile was generated. First Selenium was launched in
    interactive mode:
\begin{lstlisting}[language=sh]
java -jar $selenium.jar -interactive
\end{lstlisting}
  \item This starts an interactive prompt, a Firefox browser is then launched
    using the following command:
\begin{lstlisting}[language=sh]
cmd=getNewBrowserSession&1=*firefoxproxy&2=http://www.google.com
\end{lstlisting}
  \item This created a profile directory in /tmp. This directory is copied to a
    safe place, then all files were deleted except for \verb+cert_override.txt+
    and \verb+cert8.db+.
  \item All of the simulation sites were manually visited, with the server
    certificate being permanently accepted. This saves the certificates to
    \verb+cert_override.txt+ for future sessions.
\end{enumerate*}

To configure selenium for use in Phase 2 and 3, the file \verb+proxy.pac+ is
added to the Firefox profile with the following text:

\begin{lstlisting}[language=java]
function FindProxyForURL(url, host) {
   if(shExpMatch(host, '*torsim')) {
       return 'PROXY localhost:8118';
   }
   return 'PROXY localhost:4444; DIRECT';
}
\end{lstlisting}

This makes sure that Tor gets used for outgoing connections, and the selenium
proxy is used for running tests.

@@

\subsubsection{Server Guest}

The host system runs an Apache web server which serves two sets of sample
websites, static and dynamic. The static websites are served each from a
different numbered directory and accessible over a different virtual host. This
means that when a web browser is pointed at the host
\verb+https://site1.static.torsim/+ the files in
\verb+/var/www/thesis/experiment/simulation/static/site1+ are served to the
browser.

The dynamic web sites use Sinatra to serve content that varies over time, an
example Sinatra script for \verb+https://site59.dynamic.torsim/+ is included
below:

\paragraph{index.rb}
\lstinputlisting[language=ruby]{../experiment/simulation/site/dynamic/site59/index.rb}

\paragraph{index.haml}
\lstinputlisting[language=ruby]{../experiment/simulation/site/dynamic/site59/views/index.haml}

Each time this site is accessed it renders a random number of iframes between 1
and 20, with each iframe accessing the URI \verb+/content+ which renders between
1 and 1000 random characters. This website periodically refreshes itself every
five seconds.

\subsubsection{Tor Network Guest}

The Tor Network Guest is responsible for emulating a Tor network. It runs three
Tor directory authorities as well as fifteen relays. Tor was installed on the
Tor Network Guest using the same procedure listed in \ref{install-tor}. By
default the Tor installation runs at start time, but this is disabled by
removing execute permissions from the file \verb+/etc/init.d/tor+.

The Tor nodes are configured using the script included in the Appendix section
\ref{generate-tor-network-script}. At boot time the Tor Network Guest executes
the Run Tor Network Script included in the Appendix section
\ref{run-tor-network-script}.

@@

Running the experiment is a matter of ensuring all hardware is configured
correctly, all network connections active and all systems are powered on. Each
simulation phase was executed for two weeks without any power outages or
failures.
